### 2017-10-09 paper.tex

Despite the success of openness in software development and the curation of Wikipedia,
it is an uncommon approach in the academic instructional setting.
Each year,
thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some use textbooks written by one or a few authors,
but beyond that,
they develop and maintain their course materials in isolation.
Given that academic research often depends on sharing, the differing
approach to developing pedagogical materials is interesting,
but the sociology and psychology behind this blind spot are out of the scope of this paper.

The authors have many years of experience with community-developed lessons
in the context of research computing in the sciences and humanities
through organizations like Software Carpentry and Programming Historian.
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanities scholars.
Their guiding principles are that lessons should be:

@@

An example of how to teach these practices is Software Carpentry's (\url{https://software-carpentry.org/}) instructor training program.
First offered in 2012,
is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
This program teaches good pedagogical practices,
and introduces everyone who takes it to who Software Carpentry's lessons are for,
how they are delivered,
and how they are maintained.
Largely as a result of this training,
several hundred people per year now contribute to Software Carpentry's lessons.

@@

A key part of doing this is to create opportunities for legitimate peripheral participation.
Curating a list of small tasks that newcomers can easily tackle,
encouraging them to give feedback on proposed changes,
or asking them to add new exercises and tweak diagrams and references
can all provide an on-ramp for people who might question their own authority or ability to change the main body of a lesson.
Equally,
acknowledging all contributions,
however small,
gives new contributors an early reward for taking part. 
It can also help with the formal and informal recognition
of labour, discussed in the following rule.

>>>>

Despite the success of openness in software development and the curation of Wikipedia,
it is an uncommon approach in the academic instructional setting.
Each year,
thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some use textbooks written by one or a few authors,
but beyond that,
they develop and maintain their course materials in isolation.

Given that academic research often depends on sharing, the differing
approach to developing pedagogical materials is interesting,
but the sociology and psychology behind this blind spot are beyond the scope of this paper.

The authors have many years of experience with community-developed lessons
in the context of research computing in the sciences and humanities,
through organizations like Software Carpentry and Programming Historian.
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanities scholars.
Their guiding principles are that lessons should be:

@@

An example of how to teach these practices is Software Carpentry's (\url{https://software-carpentry.org/}) instructor training program.
First offered in 2012,
it is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
This program teaches good pedagogical practices,
and introduces everyone who takes it to who Software Carpentry's lessons are for,
how they are delivered,
and how they are maintained.
Largely as a result of this training,
several hundred people per year now contribute to Software Carpentry's lessons.

@@

A key part of doing this is to create opportunities for legitimate peripheral participation.
Curating a list of small tasks that newcomers can easily tackle,
encouraging them to give feedback on proposed changes,
or asking them to add new exercises and tweak diagrams and references
can all provide an on-ramp for people who might question their own authority or ability to change the main body of a lesson.
Equally,
acknowledging all contributions,
however small,
gives new contributors an early reward for taking part.
